---
title: "R project Crypto/Stock Return Data, Calculating Returns & Uncorrelated Clusters"
output: html_notebook
---
  
# Packages that will be used 
```{r}
install.packages("tidyverse")
install.packages("crypto2")
install.packages("lubridate")
install.packages("rvest")
install.packages("stats")
install.packages("magrittr")
install.packages("quantmod")
install.packages("tidyquant")
install.packages("dendextend")
install.packages("PortfolioAnalytics")

library(tidyverse)
library(crypto2)
library(lubridate)
library(rvest)
library(stats)
library(magrittr)
library(quantmod)
library(tidyquant)
library(dendextend)
library(PortfolioAnalytics)

```


#SECTION 1 - GET A LIST OF ALL CRYPTO TICKERS, AND THEIR PRICE HISTORY
```{r}
crypto_list()

crypto_currency <- crypto_history(limit = 1)

crypto_currency %>%
  mutate(timestamp = as.Date(as.character(timestamp))) %>%
  ggplot()+
  geom_line(aes(timestamp, close))

top_100_by_marketcap <-  
crypto_list() %>%
  arrange(rank) %>%
  slice(1:100)

top_100_by_marketcap

top_100_prices <- crypto_history(top_100_by_marketcap)

top_100_crypto_prices <-
crypto_history(top_100_by_marketcap) %>%
  mutate(timestamp = as.Date(as.character(timestamp)))



```

#SECTION 2 - CALCULATE CRYPTOCURRENCY RETURNS
```{r}

crypto_daily_returns <-
top_100_crypto_prices %>%
  arrange(symbol, timestamp) %>%
  mutate(daily_return = close/lag(close, 1)-1) %>%
  select(timestamp, name, symbol, daily_return)

crypto_daily_returns

```

#SECTION 3 - WORKING WITH HIERARCHICAL CLUSTERING ALGORITHM
```{r}

hc <-
crypto_daily_returns %>%
  pivot_wider(id_cols = timestamp, names_from = name, values_from = daily_return) %>%
  select(-timestamp) %>%
  cor(use = "complete.obs") %>%
  abs() %>%
  dist() %>%
  hclust()

hc %>%
  as.dendrogram() %>%
  plot()


number_clusters <- 4

hc %>%
  as.dendrogram() %>%
  color_branches(k = number_clusters) %>%
  color_labels(k = number_clusters) %>%
  set("labels_cex", 0.3) %>%
  # plot()
  as.ggdend() %>%
  ggplot() +
  labs(title = "Dendrogram of the top 100 Cryptocurrencies by market cap")
  

```

#SECTION 4 -CLASSIFY EACH CRYPTO INTO CORRESPONDING CLUSTER
```{r}



cutree(hc, k = number_clusters) %>%
  as.data.frame() %>%
  rename(cluster = 1) %>%
  mutate(token_name = row.names(.)) %>%
  filter(cluster == 4) #Stable coins






```

#SECTION 5 - GET ALL PRICE HISTORY FOR S&P500 COMPANIES
```{r}
tidyquant::tq_get("AAPL") %>%
  ggplot() +
  geom_line(aes(date, adjusted))


stock_table_url <- "https://en.wikipedia.org/wiki/List_of_S%26P_500_companies"


all_historical_spx_ticker <-
stock_table_url %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  extract() %>%
  html_table(fill = T)

current_spx_tickers <-
 all_historical_spx_ticker[[1]] %>%
   janitor::clean_names()

pull_all_data <- . %>% print() %>% tq_get() %>% as.data.frame()

tq_get("MMM")

"MMM" %>% pull_all_data()

all_spx_prices <-
current_spx_tickers %>%
  mutate(symbol = stringr::str_replace_all(string = symbol, pattern = "[.]", replacement = "-")) %>%
  mutate(data = map(symbol, pull_all_data)) %>%
  select(-symbol) %>%
  unnest_legacy()

all_spx_prices %>%
  select(-symbol) %>%
  unnest_legacy() %>% #pull(symbol) %>% unique
  ggplot() +
  geom_line(aes(date, adjusted, color = symbol)) +
  facet_wrap(symbol~.)

```

#SECTION 6 - PASS THEM THROUGH THE HCLUST ALGO
```{r}

wide_stock_returns <-
all_spx_prices %>%
  select(date, security, symbol, adjusted) %>%
  arrange(symbol, date) %>%
  group_by(symbol) %>%
  mutate(daily_return = adjusted/lag(adjusted)-1) %>%
  na.omit()%>%
  pivot_wider(id_cols = date, names_from = security, values_from = daily_return)


hc <-
wide_stock_returns %>%
  select(-date) %>%
  cor(use = "complete.obs") %>%
  dist() %>%
  hclust()

hc %>%
  as.dendrogram() %>%
  color_branches(k = 5) %>%
  color_labels(k = 5) %>%
  set("labels_cex", 0.3) %>%
  # plot()
  as.ggdend() %>%
  ggplot() +
  labs(title = "Dendrogram of the S&P500 Constituents")





```

#SECTION 7 - NAIVE PORTFOLIO CONSTRUCTION: RANDOMLY SELECT ONE STOCK FROM EACH CLUSTER; COMPARE A PORTFOLIO OF 1 SINGLE CLUSTER
```{r}

stock_clusters <-
cutree(hc, k = 5) %>%
  as.data.frame() %>%
  rename(cluster=1) %>%
  mutate(company_name = rownames(.))


randomly_selected_stocks <-
stock_clusters %>%
  group_by(cluster) %>%
  sample_n(size = 1)

target_cluster <- 2

individual_cluster <-
stock_clusters %>%
  filter(cluster == target_cluster) %>%
  sample_n(size = 5)

individual_cluster

randomly_selected_stocks


portfolio_1 <-
all_spx_prices %>%
  filter(security %in% randomly_selected_stocks$company_name) %>%
  arrange(symbol, date) %>%
  group_by(symbol) %>%
  mutate(closing_price = adjusted/lag(adjusted, 1)-1) %>%
  pivot_wider(id_cols = date, names_from = symbol, values_from = closing_price)


portfolio_2 <-
all_spx_prices %>%
  filter(security %in% individual_cluster$company_name) %>%
  arrange(symbol, date) %>%
  group_by(symbol) %>%
  mutate(closing_price = adjusted/lag(adjusted, 1)-1) %>%
  pivot_wider(id_cols = date, names_from = symbol, values_from = closing_price)


portfolio_1_xts <- xts(x = portfolio_1[-1], order.by = portfolio_1$date, frequency = 252)

portfolio1_returns <- Return.portfolio(portfolio_1_xts)


portfolio_2_xts <- xts(x = portfolio_2[-1], order.by = portfolio_2$date, frequency = 252)

portfolio2_returns <- Return.portfolio(portfolio_2_xts)



SharpeRatio.annualized(R = xts(x = portfolio1_returns, frequency = 252))
SharpeRatio.annualized(R = xts(x = portfolio2_returns, frequency = 252))


portfolio1_returns %>%
  as.data.frame() %>%
  mutate(date = rownames(.),
         date = ymd(date)) %>%
  rename(DiversifiedPortfolio=1) %>%
  inner_join(
    portfolio2_returns %>%
    as.data.frame() %>%
    mutate(date = rownames(.),
         date = ymd(date)) %>%
      rename(SingleClusterPortfolio=1)
  ) %>%
  arrange(date) %>%
  mutate(DiversifiedPortfolio_Cumulative = cumprod(1+DiversifiedPortfolio)-1,
         SingleClusterPortfolio_Cumalative = cumprod(1+SingleClusterPortfolio)-1) %>%
  ggplot() +
  geom_hline(aes(yintercept = 0), color = "black") +
  geom_line(aes(date, SingleClusterPortfolio_Cumalative), color = "blue") +
  geom_line(aes(date, DiversifiedPortfolio_Cumulative), color = "orange")
  labs(title = "Comparison of Portfolio Returns",
       subtitle = "Portfolio using hierarchial clustering (orange) vs. Single Cluster",
       y = "cumulative return (%)") +
    scale_y_continuous(labels = scales::percent)
  
  
  
  
  
  
Return.annualized(R = xts(x = portfolio1_returns, frequency = 252))
Return.annualized(R = xts(x = portfolio2_returns, frequency = 252))


```
